My title

### 2024-02-12 starter_folder-main 4/paper/paper.qmd
Updated future research

Recreating the Model: We will start by reproducing the competitive college market model used in the original study, ensuring our work is entirely reproducible. This step includes verifying the model's assumptions, computational methods, and data inputs.
Expanding the Study with a Canadian Lens: Specifically examine how income inequality within Canada affects university tuition, comparing these dynamics with the findings from the U.S. context. This will provide insights into how different policy environments and socio-economic conditions influence the relationship between income inequality and higher education costs.

@@

In replicating the original model by Zhifeng Cai and Jonathan Heathcote, our methodology was meticulously crafted to mirror their approach with precision, ensuring the highest degree of reproducibility. This entailed a thorough analysis of the original study's model, including its assumptions, variables, and computational methods. We closely followed the procedural steps outlined in their research, from data collection through to the analytical techniques employed to examine the relationship between income inequality and college tuition costs. To guarantee reproducibility, we documented each step of our process in detail, including the coding practices, statistical software used, and the sources of our data. This rigorous approach not only underscores our commitment to transparency and scientific integrity but also enhances the robustness and reliability of our replication efforts.

@@

## Dynamics of Canadian Universities

@@

>>>>

1. Recreating the Model: We will start by reproducing the competitive college market model used in the original study, ensuring our work is entirely reproducible. This step includes verifying the model's assumptions, computational methods, and data inputs.
2. Expanding the Study with a Canadian Lens: Specifically examine how income inequality within Canada affects university tuition, comparing these dynamics with the findings from the U.S. context. This will provide insights into how different policy environments and socio-economic conditions influence the relationship between income inequality and higher education costs.

@@

In replicating the original model by Zhifeng Cai and Jonathan Heathcote, our methodology was meticulously crafted to mirror their approach with precision, ensuring the highest degree of reproducibility. This entailed a thorough analysis of the original study's model, including its assumptions, variables, and computational methods. We closely followed the procedural steps outlined in their research, from data collection through to the analytical techniques employed to examine the relationship between income inequality and college tuition costs. To guarantee reproducibility, we documented each step of our process in detail, including the coding practices, statistical software used, and the sources of our data. This approach not only underscores our commitment to transparency and scientific integrity but also enhances the reliability of our replication efforts.

@@

## Dynamics of Canadian Universities using insights by Cai and Heathcote

@@

## Potential Weaknessess

## Future Research

Future directions should focus on closing gaps in our understanding of the dynamics between income inequality and college tuition. This involves exploring the nuanced effects of policy interventions over the long term and across diverse socio-economic groups. Researchers should consider longitudinal studies that track the impact of tuition changes on generations of students, incorporating variables like technological advancement, labor market shifts, and changing demographics. Policy-wise, a multi-faceted approach is necessary, combining financial aid adjustments, tuition regulation, and innovative funding models for higher education. Engaging with broader societal issues, such as wage stagnation and economic mobility, is crucial for creating more equitable access to higher education.

Like mentioned in the paper, Cai and Heathcote acknowledges the limitations of using a perfectly competitive model to understand real-world educational markets, where competition among colleges is imperfect and how colleges might use financial aid information to offer less aid to students from wealthier families, particularly at more selective institutions, suggesting these colleges possess significant pricing power. To delve deeper into these complexities, the passage proposes several research extensions such as modeling colleges with unique attributes like location or brand name that could justify differential pricing and attract students with specific preferences. They also raise the idea of exploring how colleges' limited information about applicants' abilities affects students' strategies in applying to multiple institutions. It advocates for broadening the scope of attributes considered in college admissions to include the value of diversity, potentially altering the competitive landscape for colleges seeking to attract students from varied backgrounds. By examining how changes in the value placed on college quality could affect income inequality and intergenerational mobility over time. They hypothesizes that an increase in the financial returns from attending high-quality colleges could lead to greater investment in such education by wealthier families, thereby exacerbating income inequality and reducing social mobility across generations.
